### 2013-04-03 R/reportmd.Rmd
new reports including contacts, references

@@

@@

### Species - please provide any missing information

The dataset includes `r length(unique(.dat$data$species))` species belonging to `r length(unique(.dat$data$family))` families, presenting `r length(unique(.dat$data$pft))` functional types, growing in `r length(unique(.dat$data$growingCondition))` conditions within `r length(unique(.dat$data$vegetation))` major types of habitat:
```{r echo=FALSE, message=FALSE, warning=FALSE, comment=''}
fam.spec(.dat$data)
```

>>>>

Study reference: `r .dat$ref`

Study contact: `r .dat$contact$name`.

Contact email: `r .dat$contact$email`.

Contact address: `r .dat$contact$address`.

Data description
-----------------------------------

@@

The dataset includes `r length(unique(.dat$data$species))` species belonging to `r length(unique(.dat$data$family))` family(ies), presenting `r length(unique(.dat$data$pft))` functional type(s), growing in `r length(unique(.dat$data$growingCondition))` condition(s) within `r length(unique(.dat$data$vegetation))` major type(s) of habitat:

@@

### Location level - please provide any missing information
```{r echo=FALSE, message=FALSE, warning=FALSE, comment=''}
locLevelInfo(.dat$data)
```

### Stand level - please provide any missing information
```{r echo=FALSE, message=FALSE, warning=FALSE, comment=''}
standLevelInfo(.dat$data)
```

### Species level - please provide any missing information
```{r echo=FALSE, message=FALSE, warning=FALSE, comment=''}
spLevelInfo(.dat$data)
```

### Method - please provide any missing information/follow template
```{r echo=FALSE, message=FALSE, warning=FALSE, comment=''}
printMeta(.dat$data)
```
